### 2014-06-03 ACL2014/discussion.tex

Yet another application is removing duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences 
would be distracted from ``duplicated results.'' 
That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
to find ``duplicated query terms'' efficiently. As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

We first described the existing ``vanilla'' \lsh algorithm. It is the first paper according to 
best of our knowledge that applies this algorithm to NLP applications. 
Next, we poposed four novel variants of vanilla \lsh. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

>>>>

Yet another application is removing duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences 
would be distracted from ``duplicated results.'' 
That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
to find ``duplicated query terms'' efficiently. As ``duplicates'' among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

We first described the existing ``vanilla'' \lsh algorithm. It is the first paper according to 
best of our knowledge that applies this algorithm to NLP applications. 
Next, we proposed four novel variants of vanilla \lsh. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.
